
Load of packages and set crayola data
```{r}

library(rvest)
library(colorspace)
library(dplyr)
library(reshape2)
library(plotly)

crayonURL <- "https://en.wikipedia.org/wiki/List_of_Crayola_crayon_colors"

```


Load in Wikipedia crayola colors. There are way more than 64 and it includes older versions of crayons!
```{r}

temp <- crayonURL %>% 
  read_html %>%
  html_nodes("table")

all_crayons <- html_table(temp[[1]]) %>% mutate(Color = tolower(gsub("[^a-zA-Z0-9]","",Color)), Hexadecimal = substr(Hexadecimal, 1,7))

```


Take list of colors in 64-pack and add data from the larger Wikipedia table. Fix individual cases of name changes or updated colors.
```{r}

pack_64 <- read.csv("~/Desktop/crayola_colors.csv",header = F, col.names = "Color") %>% mutate(Color = tolower(gsub("[^a-zA-Z0-9]","",Color))) %>% left_join(all_crayons)

pack_64[pack_64$Color == "violet",2:ncol(pack_64)] <- all_crayons[all_crayons$Color=="violetii",2:ncol(pack_64)]

pack_64[pack_64$Color == "blue",2:ncol(pack_64)] <- all_crayons[all_crayons$Color=="blueiii",2:ncol(pack_64)]

pack_64[pack_64$Color == "chestnut",2:ncol(pack_64)] <- all_crayons[all_crayons$Color=="indianred",2:ncol(pack_64)]

pack_64[pack_64$Color == "gold",2:ncol(pack_64)] <- all_crayons[all_crayons$Color=="goldii",2:ncol(pack_64)]

pack_64[pack_64$Color == "lavender",2:ncol(pack_64)] <- all_crayons[all_crayons$Color=="lavenderii",2:ncol(pack_64)]

pack_64$num_range <- seq(1,nrow(pack_64))

```


Take the given hex code values and change them into LAB triplets
```{r}

x <- hex2RGB(pack_64$Hexadecimal, gamma = FALSE)
storage.mode(x@coords) <- "numeric" # as(..., "LUV") doesn't like integers for some reason
y <- as(x, "LAB")
DF <- as.data.frame(y@coords)

```


Plot the colors in 3D CIELab colorspace with marker colors set to their hex codes. Publish and open in Plotly.
```{r}
p <- plot_ly(DF, x = ~B, y = ~A, z = ~L, 
             marker = list(color = ~col, colorscale = col)) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'b*'),
                      yaxis = list(title = 'a*'),
                      zaxis = list(title = 'L*')))

chart_link <- plotly_POST(p, filename="crayola_64_pack")
chart_link
```



