
Load of packages and set crayola data
```{r}
packrat::on()
library(rvest)
library(colorspace)
library(tidyverse)
library(magrittr)
library(plotly)

crayonURL <- "https://en.wikipedia.org/wiki/List_of_Crayola_crayon_colors"

```


Load in Wikipedia crayola colors. There are way more than 64 and it includes older versions of crayons!
```{r}

temp <- crayonURL %>% 
  read_html %>%
  html_nodes("table")

all_crayons <- html_table(temp[[1]])

names(all_crayons) <- tolower(names(all_crayons))

all_crayons %<>%
  mutate(color = tolower(gsub("[^a-zA-Z0-9]","",color)), hexadecimal = substr(hexadecimal, 1,7))

```


Take list of colors in 64-pack and add data from the larger Wikipedia table. Fix individual cases of name changes or updated colors.
```{r}

pack_64 <- read_csv("~/Desktop/crayola_colors.csv", col_names = c("color", "id")) %>% mutate(color = tolower(gsub("[^a-zA-Z0-9]","",color))) %>% left_join(all_crayons)

pack_64[pack_64$color == "violet",3:ncol(pack_64)] <- filter(all_crayons, color == "violetii") %>% select(-color)

pack_64[pack_64$color == "blue",3:ncol(pack_64)] <- filter(all_crayons, color == "blueiii") %>% select(-color)

pack_64[pack_64$color == "chestnut",3:ncol(pack_64)] <- filter(all_crayons, color == "indianred") %>% select(-color)

pack_64[pack_64$color == "gold",3:ncol(pack_64)] <- filter(all_crayons, color == "goldii") %>% select(-color)

pack_64[pack_64$color == "lavender",3:ncol(pack_64)] <- filter(all_crayons, color == "lavenderii") %>% select(-color)

```


Take the given hex code values and change them into LAB triplets
```{r}

x <- hex2RGB(pack_64$hexadecimal, gamma = FALSE)
storage.mode(x@coords) <- "numeric" 
y <- as(x, "LAB")
pack_64 %<>% 
  left_join(as.data.frame(y@coords) %>% mutate(id = row_number())) 
names(pack_64) <- tolower(names(pack_64))

write_csv(pack_64,"data/crayola_color_coordinates.csv", na="")

```


Plot the colors in 3D CIELab colorspace with marker colors set to their hex codes. Publish and open in Plotly.
```{r}
p <- plot_ly(DF, x = ~B, y = ~A, z = ~L, 
             marker = list(color = ~col, colorscale = col)) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'b*'),
                      yaxis = list(title = 'a*'),
                      zaxis = list(title = 'L*')))

chart_link <- plotly_POST(p, filename="crayola_64_pack")
chart_link
```



